---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AUCst

<!-- badges: start -->
<!-- badges: end -->

Simulated example dataset and sample code for calculating the two-dimensional AUC for one longitudinal biomarker, under the regular visit scenario.

## Installation

You can install the development version of AUCst like so:

``` r
library(devtools)
install_github("JingZ2021/AUCst",force = TRUE)
library(AUCst)
```

## Example

R file contians functions used to implement the proposed method.

```{r}
library(AUCst)
## basic example code
da.sim.short <- AUCst::da.sim.short
da.sim.long <- AUCst::da.sim.long
sort(unique(da.sim.long$vtime))  
obj.i=AUCst::main1.sub.func(da=da.sim.short, 
                            da.long=da.sim.long,
                            sk=c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1, 1.1, 1.2), 
                            tseq.eval=c(0.4,1.11,1.50,1.90), resample =1, nsap=3)
obj.i$AUC          
obj.i$theta
obj.i$SE
obj.i$conv
```

## Reference

Zhag, J., Ning, J., Huang X., & Li R. (2021). On the Time-varying Predictive Performance of Longitudinal Biomarkers: Measure and Estimation. Statistics in Medicine,
40(23):5065-5077. <https://doi.org/10.1002/sim.9111>
